The Folly of Password Policies: The case for organisations implementing technical alternatives over trying to manage users

### 2014-12-15 paper.tex
Cut a bit more...

Passwords are not the only approach to verifying a user's identity.
The methods by which a user can be authenticated are known to fall
into three categories -- or \emph{factors} -- of authentication
\parencite{council2005authentication}:

\begin{itemize}
  \item something the user \emph{knows}, such as a password, a PIN or
    personal information (e.g. mother's maiden name);
  \item something the user \emph{has}, such as a passport, a mobile device
    a paper ticket; and
  \item something the user \emph{is}, such as their DNA sequence,
    their retinal pattern, their fingerprint.
\end{itemize}

It should be noted that some methods can be argued as spanning
over two factors. For example, a credit card is something
a bank customer possesses, but the card number is something
an attacker could learn without the owner losing ownership
of the card. In the context of many online purchase, credit
card \emph{details} arguably become something a user \emph{knows}.

There
has been a rise in two-factor authenication with companies
such as Google, Amazon, Microsoft, Paypal and Twitter having enabled
two-factor authentication for user accounts.

@@

Brute-force password guessing can also be mitigated by
users changing passwords frequently enough that attackers
have a short window within which to guess a particular
password.

@@

Some of the identified alternatives to password authentication were
evaluated for use in an organisational setting. The focus of this evaluation
was to run through the steps involved in creating a toy network of machines
that allowed common authentication across a representative sample of
classes of services that may be used by businesses.

The requirements for our toy/proof-of-concept systems were:

\begin{itemize}
  \item \textbf{Desktop Login}: users can sign into desktop machines using the authentication method
    being evaluated;
  \item \textbf{Company Email}: users can then access their corporate email without additionally
    supplying a password to do so;
  \item \textbf{Web Login}: users are able to sign in to a dummy web service (a simple static page
    behind an authentication layer was used);
  \item \textbf{SSH Login}: users should be able to do remote SSH login to development Unix
    servers (this assumes a company where this is a common work task, e.g.
    software development, which is included to exercise the authentication
    further rather than to act as a typical business use case).
\end{itemize}

>>>>

Passwords are not the only approach to verifying a user's identity.
There
has been a rise in two-factor authenication with companies
such as Google, Amazon, Microsoft, Paypal and Twitter having enabled
two-factor authentication for user accounts. Examples include One-Time
Passwords or challenge-response codes.

@@

@@

Some of the identified alternatives to password authentication were
evaluated for use in an organisational setting.
The requirements for our toy/proof-of-concept systems were:

\begin{itemize}
  \item \textbf{Desktop Login}: users can sign into desktop machines using the authentication method
    being evaluated;
  \item \textbf{Company Email}: users can then access their corporate email without additionally
    supplying a password to do so;
  \item \textbf{Web Login}: users are able to sign in to a dummy web service (a simple static page
    behind an authentication layer was used);
  \item \textbf{SSH Login}: users should be able to do remote SSH login to development Unix
    servers (this assumes a company where this is a common work task, e.g.
    software development)
\end{itemize}
